\documentclass[twocolumn]{article}
\usepackage[utf8]{inputenc}

\usepackage[letterpaper]{geometry}

\usepackage{setspace}

% An easier to read font
\renewcommand{\familydefault}{\sfdefault}
\usepackage[normalem]{ulem}

% Set margins
\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in}

\renewcommand{\thesection}{}
\renewcommand{\thesubsection}{}
\renewcommand{\thesubsubsection}{}

% Title, Author, Date
\title{Technical Resume}
\author{Christine Dodrill \textless{}sam@dodrill.net\textgreater{}}
\date{}

\begin{document}

% Munge the title for Two-column
\twocolumn[
 \begin{@twocolumnfalse}
  \maketitle
   \end{@twocolumnfalse}
]

\section{Open Source Projects}

\subsection{Duta}

Duta is an attempt to create a more modern, scalable standard for IRC client communications.  This is a new client protocol designed to replace the standard RFC 1459 protocol while still maintaining compatibility with the older protocol via server links. The general format is identical to the TS6 link protocol. This is unfortunately a requirement because if the fundamental problems in the IRC client protocol.

Clients are expected to know information about:

\begin{itemize}
	\item Channels
	\item Clients
	\item Limited info about servers
\end{itemize}

All clients are identified by a unique identifier. Information about each client is broadcast in a \texttt{CLIENT} line that describes the client to the user. An example of such a \texttt{CLIENT} line is shown below, along with the format of it:

\begin{verbatim}
:<server id> CLIENT <nick> <ident>
  <display host> <uid>
  <account name or *> 
  <* if staff, C if not> <timestamp> 
  :<real name>
\end{verbatim}

or for a more real world example:

\begin{verbatim}
:420 CLIENT Xena xena yolo-swag.com
  420AAAAAB Xena * 1234567890
  :Xena
\end{verbatim}

RFC 1459 \texttt{MODE} will be broken up into 4 separate commands, \texttt{PROP}, \texttt{STATUS}, \texttt{LIST}, and \texttt{UPROP}.

\vspace{0.125in}

\begin{tabular}{| l | l |}
	Verb & Use \\
    \hline
    \texttt{PROP} & Set channel properties \\
    \texttt{STATUS} & Change rank of clients in a channel \\
    \texttt{LIST} & Change channel lists, such as the \\
                  & list of banned users \\
    \texttt{UPROP} & Change user proprerties (analogous to \\
                   & RFC 1459 user modes) \\
\end{tabular}

There are many other benefits to this new protocol; \texttt{account-notify}, \texttt{away-notify}, \texttt{multi-prefix} and other simple IRCv3 client capabilities will be core parts of the protocol and parsing them will be required to avoid fragmentation.

Registering a connection with the IRC daemon is now also a lot less stateful and will require only one command from a client instead of two as RFC 1459 mandates.

If a user gets a private message or notice from a client it doesn't previously knowledge about (services, random messages, etc) it must send a \texttt{CLINFO} line to the server requesting information on the client as identified by its UID.

Because the users are all identified by their UID and the UID is made up of the Server ID plus a unique number (constantly incrementing), a netsplit can be broadcast to clients only in the form of a server ID quitting. This will also save a lot of bandwidth as netsplit quit messages can get costly quick. It would be:

\begin{verbatim}
:420 NETSPLIT 450 :*.net *.split
\end{verbatim}

instead of sending something like this for every client lost in the split:

\begin{verbatim}
:Tekner!user@legendsofequestria.com
  QUIT :*.net *.split
\end{verbatim}

\subsection{Cod}

Cod is an extended services package for IRC networks using TS6 family IRC daemons. It is designed to be very modular, allowing some networks to only enable what they will need, but also to handle some things normally handled by channel bots. This works symbiotically with Elemental-IRCd.

Over the last 5 months of writing this project mostly from scratch (some module code is recycled from other projects or has turned into other projects), I have learned more about program design and modular management. I also learned how to properly use \texttt{select()} and made Cod asynchronous without affecting too many other parts of the core.

\subsection{Elemental-IRCd}

Elemental-IRCd is a fork of the (now defunct) ShadowIRCd project. It is also a fork of Atheme's Charybdis irc daemon with more user-friendly features. Most of these things are security patches, network staff usability features, patches that make centralized management simpler and extra status levels in channels; but the resulting core changes mean it needs to be its own project.

At one point I wrote up something to the Full-Disclosure mailing list about a bug I found in its upstream ShadowIRCd, a temporary fix, and why the bug could cause the entire network to segfault if a malicious user sent a specially crafted SASL authentication session. You can find my writeup on it, including full exploit code and debugging information on the Full-Disclosure archive: http://seclists.org/fulldisclosure/2014/Mar/320 Since the full-disclosure email was sent, a full patch has been contributed and accepted into the main tree.

\subsection{ircmess}

When writing Cod I wrote a custom IRC line parser. After realizing it would be useful in my other projects, I packaged it up in the cheese shop. You can install it with \texttt{pip install ircmess} or see more information about it here: https://github.com/lyska/ircmess

\subsection{Tetra}

Tetra is the next generation of Cod. I have thrown around rewriting Cod several times to fix a lot of the design and core issues with it that I had not realized until far far too late as well as write it to be more parallel than the previous iteration. The core of Tetra is in Go and the scripts are all written in either Lua or Moonscript. It also keeps statistics and does some other, more experimental things like Bayesian spam filtering.

Tetra is not yet mature enough to be used in production, but given time (and a few iterations on the core design) it will be. I have documentation written as I am developing but a fair bit of the core needs to be separated out into discrete modules to allow for tests to be written.

You can find out more about Tetra by visiting http://github.com/Xe/Tetra.

\section{Devops}

\subsection{OpDemand}

For a while I had worked under the excellent folks at OpDemand on their flagship product Deis, a Heroku-like PaaS backed by CoreOS, Docker and etcd. Here I learned a lot about scalable systems design as well as maintence programming on a polyglot project.

\subsection{Personal}

I maintain a personal fork of Dokku, Progrium's single server PaaS that I use on my Singapore DO node \textit{dokku.xeserv.us}. I use this for various personal projects or other things that need a home that I can easily set up and forget about.

I also do production operations for a variety of personal projects, one of which is the ShadowNET Internet Relay Chat network. This network was set up as a test network for Elemental-IRCd, Cod and Tetra and has become a home of a tight-knit group of my friends.

\section{Testing}

\subsection{Microsoft}

I have worked for a year with Volt doing hardware testing for Microsoft. I am currently under a strict NDA because of this, but I am allowed to tell you it was for the Xbox series of game consoles.

\section{Academics}

\subsection{Classes Taken}

\subsubsection{Eastern Washington University}

\begin{tabular}{| l | r |}
    Class & Date \\
    \hline
    Algorithms & Winter 2012 \\
    C \& Unix & Spring 2012 \\
    Data Structures & Spring 2012 \\
    Discrete Mathematics & Winter 2011 \\
    Java I \& II & Fall/Winter 2010 \\
\end{tabular}

\section{Employment History}

\begin{tabular}{| l | l | r | l |}
    Company & Role & Dates \\
    \hline
    Symplicity & Junior SA & 11/13-01/14 \\
    Microsoft & Quality Assurance & 06/12-09/13
\end{tabular}

\section{Other Honors}

\begin{tabular}{| l | r |}
    Description & Date \\ \hline
    Lead of Programming Team & 9/10-3/11 \\ 
    for HS Robotics Team & \\ \hline
    Personal Server Administration & 06/11-  \\ \hline
    Beta Tester for Google Chrome OS & 12/11-06/12 \\ \hline
    Video Encoding & 01/12- \\
\end{tabular}

\end{document}
